\section{Failures of Word}

In case it is not clear how unstable, buggy, and annoying Word is, I have included a few oddities and frustrations of Word below:

\begin{itemize}
	\item Tables split across page breaks by default.
	\item Captions are not attached to the corresponding object by default.
	\item Sometimes invisible, unselectable, and undeletable formatting characters can appear in your document that break your formatting. The only fix for this is manoeuvering the character somewhere it does no harm, or copying everything into a new document.
	\item Clicking the bullet point button can change the font size and font style.
	\item Space after paragraph should be used to ensure space between paragraphs, but the space is still added for the last paragraph on the page. As the space is attached to the paragraph, it puts the line on the next page even if that line would fit above. To avoid widows, space after paragraph needs to be manually handled.
	\item The gap between ``Figure" or ``Table" and the number in the caption is not a non-breaking space by default. When cross-referencing this can result in the number being on a new line.
	\item Vertically centred text in a cell of a table does not appear vertically centred, even if space before and after paragraph and margins are symmetrical.
	\item Page breaks take up space. This means if the last line that fits on the page is long then the page break mark is moved to the next page, meaning a blank page. This means needing to manually handle the page break.
	\item Changing the width of a column in a table where the last cell highlighted is merged will only change the width of the first row of the merged cell. This means needing to change the width of those cells separately and remerging afterwards.
	\item The number of words that fit on a line depends on their justification - this should only affect the spacing between words (unless rivers are avoided, which Word cannot do).
\end{itemize}